Who does big team science?

### 2023-04-06 manuscript_scopus.Rmd
fixes

label_expressions <- function(values) {
  stopifnot(is.expression(values))
  as_labeller(function(x) {
    if (is.null(names(values))) {
      x <- seq_along(x)
      if (length(x)!=length(values)) warning(paste0("Number of labels(", 
        length(values), ") does not match number of values (", length(x), ")"))
    }
    as.list(values[x])
  }, default=identity)
}

@@

```{r results = 'asis', include = TRUE}
flextable(
  DF$snip %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum))
)
```

@@

```{r results = 'asis', include = TRUE}
flextable(
  DF$snip_all %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum))
)
```

@@

@@

@@

ggplot(avg_author_time, aes(Year, Average_Num_Authors)) + 
  theme_classic() + 
  geom_point(aes(size = Number_Papers)) + 
  #geom_point() + 
  #geom_pointrange(aes(ymin = low, ymax = high)) + 
  facet_wrap(~SubjectArea) + 
  ylab("Average Number of Authors") + 
  xlab("Publication Year") + 
  theme(legend.position = "none")
```

@@

```{r}
ggplot(DF$career_time %>% 
         filter(SubjectArea != "Multidisciplinary"), 
       aes(Year, avg_career, color = sd_career)) +
  theme_classic() + 
  geom_point() +
  facet_wrap(~SubjectArea) + 
  theme(legend.position = "non") + 
  ylab("Average Career Length") +
  xlab("Year of Publication")
```

@@

@@

```{r}
pub_types <- bind_rows(
  DF$pub_types %>% mutate(type = "Big Team"), 
  DF$normal_pub_type %>% mutate(type = "Normal")
)

@@

@@

end up with a list of effect sizes by year by small medium large 
x axis is year
y axis is the effect size and the confidence interval 
if diversity is increasing then the patterns would be more similar (effect size of zero)
if diversity is not increasing then the patterns would be different (effect size does not include zero)

who is not represented in the "corresponding" spots - proportion chart by decades stacked bar chart of the decades

>>>>

label_expressions <- function(values) {
  stopifnot(is.expression(values))
  as_labeller(function(x) {
    if (is.null(names(values))) {
      x <- seq_along(x)
      if (length(x)!=length(values)) warning(paste0("Number of labels(", 
        length(values), ") does not match number of values (", length(x), ")"))
    }
    as.list(values[x])
  }, default = identity)
}

@@

```{r results = 'asis', include = TRUE}
flextable(
  DF$snip %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum))
)
```

@@

```{r results = 'asis', include = TRUE}
flextable(
  DF$snip_all %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum))
)
```

@@

#### REDO THIS WITH QUANTEDA ####

@@

##### FIX CAPTIONS #####

@@

ggplot(avg_author_time, aes(Year, Med_Num_Authors)) + 
  theme_classic() + 
  geom_point(aes(size = Number_Papers)) + 
  geom_point(aes(Year, Average_Num_Authors, color = "red")) + 
  #geom_pointrange(aes(ymin = low, ymax = high)) + 
  facet_wrap(~SubjectArea) + 
  ylab("Average Number of Authors") + 
  xlab("Publication Year") + 
  theme(legend.position = "bottom")
```

@@

```{r}
ggplot(DF$career_time %>% 
         filter(SubjectArea != "Multidisciplinary"), 
       aes(Year, avg_career, color = sd_career)) +
  theme_classic() + 
  geom_point(aes(size = num_papers)) +
  facet_wrap(~SubjectArea) + 
  theme(legend.position = "bottom") + 
  ylab("Average Career Length") +
  xlab("Year of Publication")
```

@@

#### MOVE R2 to the right #####

@@

```{r}
pub_types <- bind_rows(
  DF$pub_types %>% mutate(type = "Big Team"), 
  DF$normal_pub_type %>% mutate(type = "Normal")
) %>% 
  filter(publication_type == "ar" | publication_type == "pp" | 
           publication_type == "dp")

@@

#### four panel plot with tree and country next to each other ####

@@
